An enhancer code compendium of early human neuronal and neural crest development

### 2025-04-08 manuscript.tex
Typo

We built a compendium of enhancer-codes underlying early human neuronal and neural crest development. P
roviding enhancer-codes of neuronal progenitor DV- and AP-patterning, 
early neuronal fate acquisition and 
neural crest induction, migration and facial mesenchyme specification.\par

>>>>

We built a compendium of enhancer-codes underlying early human neuronal and neural crest development. 
Providing enhancer-codes of neuronal progenitor DV- and AP-patterning, 
early neuronal fate acquisition and 
neural crest induction, migration and facial mesenchyme specification.\par
